Manuscript progress report

### 2024-01-02 Docs/manuscript.Rmd
edit manuscript progress report

```{r binning}
df_nhanes %>% select(SEQN, Z, sind) %>% 
  filter(SEQN %in% rand_id3 & sind >= 650 & sind <= 750) %>% 
  mutate(SEQN = as.factor(SEQN)) %>% 
  ggplot()+
  geom_point(aes(x=sind, y = Z, col = SEQN), size = 0.5)+
  geom_vline(xintercept = seq(650, 750, by = 10), linetype="dashed")+
  scale_y_continuous(breaks = c(0, 1))+
  labs(x="Time", y="", title = "NHANES binary activity indicator")
```

```{r}
df_fig <- df_nhanes %>% select(SEQN, Z, sind) %>% 
  filter(SEQN %in% rand_id3 & sind >= 650 & sind <= 750) %>% 
  mutate(bin = cut(sind, breaks = seq(650, 750, by = 10), 
                   labels = seq(655, 745, by = 10),
                   include.lowest = T)) 
bin_mid <- seq(655, 745, by = 10)

@@

```{r}
df_nhanes_cont <- readRDS(here("Data/NHANES_AC_processed.rds"))
p_cont <- df_nhanes_cont %>% 
  filter(SEQN %in% sample(unique(df_nhanes_cont$SEQN), 4) & WEEKDAY==6) %>% 
  select(starts_with("min"), SEQN) %>%
  pivot_longer(1:1440, names_to = "Minute") %>% 
  mutate(Minute = gsub("MIN", "", Minute)) %>%
  mutate(Minute = as.numeric(Minute),
         SEQN=as.factor(SEQN)) %>%
  ggplot(aes(x=Minute, y=value, col=SEQN))+
  geom_point(size = 0.5, alpha=0.5)+
  geom_smooth(se=F, size = 0.5)+
  scale_x_continuous(breaks = seq(0, 1440, by = 480),
                     labels = c("Midnight", "8am", "4pm", "Midnight"))+
  theme(axis.text = element_text(size = 5))+
  labs(y="", title = "NHANES Activitiy count (2003-2004)")
```

```{r}
# a example of continuous and binary NHANES data
p_bi <- df_nhanes %>% select(SEQN, Z, sind) %>% 
  filter(SEQN %in% rand_id3 & Z == 1) %>% 
  mutate(SEQN = as.factor(SEQN)) %>% 
  ggplot()+
  geom_point(aes(x=sind, y = SEQN), size = 0.5)+
  scale_x_continuous(breaks = seq(0, 1440, by = 480),
                     labels = c("Midnight", "8am", "4pm", "Midnight"))+
  theme(axis.text = element_text(size = 5))+
  labs(x="Time", y="Subject", title = "NHANES binary activity indicator (2011-2014)")
```

```{r data_exp, fig.height=4, fig.width=10}
ggarrange(p_cont, p_bi, nrow = 1)
```

@@

```{r dynpred_exp,  fig.height=4, fig.width=10}
ggarrange(
  pred_list_all[[1]] %>% 
    filter(id==501) %>%
    mutate(eta_i = ifelse(t<=0.2, eta_i, NA)) %>%
    ggplot()+
    geom_line(aes(x=t, y=eta_i, col = "Observed"), na.rm = T)+
    geom_line(aes(x=t, y=pred0.2, col = "Predicted"), na.rm = T, 
              linetype = "dashed")+
    geom_vline(xintercept = 0.2, linetype = "dashed")+
    labs(x="Time", y="")+
    scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
    theme(axis.text = element_text(size = 5))+
    ylim(-1.2, 1.7),

>>>>

```{r binning, eval=FALSE}
df_nhanes %>% select(SEQN, Z, sind) %>% 
  filter(SEQN %in% rand_id3 & sind >= 650 & sind <= 750) %>% 
  mutate(SEQN = as.factor(SEQN)) %>% 
  ggplot()+
  geom_point(aes(x=sind, y = Z, col = SEQN), size = 0.5)+
  geom_vline(xintercept = seq(650, 750, by = 10), linetype="dashed")+
  scale_y_continuous(breaks = c(0, 1))+
  labs(x="Time", y="", title = "NHANES binary activity indicator")
```

```{r,eval=FALSE}
df_fig <- df_nhanes %>% select(SEQN, Z, sind) %>% 
  filter(SEQN %in% rand_id3 & sind >= 650 & sind <= 750) %>% 
  mutate(bin = cut(sind, breaks = seq(650, 750, by = 10), 
                   labels = seq(655, 745, by = 10),
                   include.lowest = T)) 
bin_mid <- seq(655, 745, by = 10)

@@

```{r, eval=FALSE}
df_nhanes_cont <- readRDS(here("Data/NHANES_AC_processed.rds"))
p_cont <- df_nhanes_cont %>% 
  filter(SEQN %in% sample(unique(df_nhanes_cont$SEQN), 4) & WEEKDAY==6) %>% 
  select(starts_with("min"), SEQN) %>%
  pivot_longer(1:1440, names_to = "Minute") %>% 
  mutate(Minute = gsub("MIN", "", Minute)) %>%
  mutate(Minute = as.numeric(Minute),
         SEQN=as.factor(SEQN)) %>%
  ggplot(aes(x=Minute, y=value, col=SEQN))+
  geom_point(size = 0.5, alpha=0.5)+
  geom_smooth(se=F, size = 0.5)+
  scale_x_continuous(breaks = seq(0, 1440, by = 480),
                     labels = c("Midnight", "8am", "4pm", "Midnight"))+
  theme(axis.text = element_text(size = 5))+
  labs(y="", title = "NHANES Activitiy count (2003-2004)")
```

```{r, eval=FALSE}
# a example of continuous and binary NHANES data
p_bi <- df_nhanes %>% select(SEQN, Z, sind) %>% 
  filter(SEQN %in% rand_id3 & Z == 1) %>% 
  mutate(SEQN = as.factor(SEQN)) %>% 
  ggplot()+
  geom_point(aes(x=sind, y = SEQN), size = 0.5)+
  scale_x_continuous(breaks = seq(0, 1440, by = 480),
                     labels = c("Midnight", "8am", "4pm", "Midnight"))+
  theme(axis.text = element_text(size = 5))+
  labs(x="Time", y="Subject", title = "NHANES binary activity indicator (2011-2014)")
```

```{r data_exp, fig.height=4, fig.width=10, eval=FALSE}
ggarrange(p_cont, p_bi, nrow = 1)
```

@@

```{r dynpred_exp,  fig.height=4, fig.width=10, eval=FALSE}
ggarrange(
  pred_list_all[[1]] %>% 
    filter(id==501) %>%
    mutate(eta_i = ifelse(t<=0.2, eta_i, NA)) %>%
    ggplot()+
    geom_line(aes(x=t, y=eta_i, col = "Observed"), na.rm = T)+
    geom_line(aes(x=t, y=pred0.2, col = "Predicted"), na.rm = T, 
              linetype = "dashed")+
    geom_vline(xintercept = 0.2, linetype = "dashed")+
    labs(x="Time", y="")+
    scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
    theme(axis.text = element_text(size = 5))+
    ylim(-1.2, 1.7),
